\section{Previous/Current Employment}
% Reformat and make it  more readable and make the points pop so that it can be seen at a glance.


\newcommand{\job}[3]{\textbf{\color{color1}#1,} \textit{#2} \hfill  \textbf{#3}}
\setlist[itemize]{leftmargin=1cm}

\nonbox{
\job{Software Engineer}{Apr. 2023 - present}{Ascend Analytics}
\begin{itemize}
        \item Developed software solutions for energy market research, in an Agile environment.
        \item Created data pipelines to extract, transform, and load data from diverse sources, including public databases and private APIs.
        \item Maintained, tested, and designed high performance REST API endpoints for data processing and retrieval.
        \item Debugged and refactored derelict code, resulting in over 10x speed improvements to the retrieval of critical information.
        \item Worked with energy managers, utility operators, and data aggregators to ensure the quality, and accuracy of pricing and energy data.
\end{itemize}
}

\shadebox{
\job{Research Software Engineer}{Apr. 2021 - Apr. 2023}{Colorado State
University}
\begin{itemize}
        \item Lead developer of DRAM, a framework for exploring genetic data.
        \item Lead developer and designer of DRAM2, a massive upgrade to DRAM with 50\%+ original code and 30\% original features, huge 10x speed improvements, and distributed computing support.
        \item Created complex, fully custom data visualizations for highly unique datasets.
        \item Responded to and closed 100+ issues for lab maintained FOSS projects.
        \item Maintained Code base, Documentation, Code Quality Statistics, and Continues Integration.
        \item Presented work in posters and presentations including at international conferences.
        \item Created 5 large scale complex ETL pipelines in Python, Snakemake, and BASH. Automated multi-day process, standardizing protocols, and maximizing use of HPC systems.
        \item Developer of KB-dram, a separate version of dram meant to run on the K-base platform in collaboration with the KBase team. Restoring functionality in a changing API. % This included maintaining a separate UI and managing issues unique to the environment and users.
        \item Co-maintained tools on the CSU HPC, and other HPC systems, and provided troubleshooting via GitHub.
        \item Worked with students and experts specializing in multiple disciplines, to collect, process and present key data and findings.
        \item Supported Students and postdoctoral staff by developing and communicating solutions data science, machine learning, and statistical tasks.
\end{itemize}
}

\nonbox{
\job{Machine Learning Engineer}{Dec. 2020 - Apr. 2021}{Biointellisense}
\begin{itemize}
\item Developed machine learning and time series models, processing data for wearable devices.
\end{itemize}
}

\shadebox{
\job{Machine Learning Graduate Apprentice}{Jan. 2020 - Dec. 2020}{University of Colorado Denver}
\begin{itemize}
\item Created documentation and tools to securely manage and analyze a large genetic data set.
\item Designed an original algorithm, implemented in Python, to address the challenge of imbalanced classes in genetic data.
%\item Utilized HPC resources and state-of-the-art hardware to build, fit, and evaluate custom and off the shelf models.
\item Utilized HPC resources to build, fit, and evaluate custom and off-the-shelf models.
\item Communicated findings and research to advisors of diverse backgrounds through presentations and reports.
\end{itemize}
}

\nonbox{
\job{Teaching Assistant (Algorithms)}{Aug. 2019 - Dec. 2019}{University of Colorado Denver}
\begin{itemize}
% \item Responsible for assisting students with class comprehension and programming tasks, and grading Python assignments.
\item Assisted students with class comprehension, graded written and Python programming assignments.
\end{itemize}
}


\shadebox{
\job{Graduate Intern}{May 2019 - Aug. 2019}{National Renewable Energy Lab (NREL)}
\begin{itemize}
%\item Created a complex Python package for processing, converting, and transforming energy data sets enabling NREL research.
\item Created a complex Python package for importing, cleaning, and transforming data from partner institutions to ensure compatibility with NREL tools.
\end{itemize}
}

%\cventry{May 2019 - August 2019}{Graduate Intern}{National Renewable Energy Lab}{}{}
%    {
%\bdot
%}
\nonbox{
\job{Research Associate}{Mar. 2016 - Aug. 2018}{BBC Research and Consulting}
%    \cventry{March 2016 - August 2018}{Research Associate}{BBC Research and Consulting}{}{}
%    %{\vspace{3pt}Responsible for gathering information, analyzing data, and automating processes for economic and social science. Working with large relational databases by cleaning, proofing, and analyzing the data therein. Also acquire secondary data sets from corporate, government, and academic sources. Accomplishing tasks with a tool kit including R, Perl, SQL, VBA, and others.}
%    {
%As a Research Associate: \\
\begin{itemize}
% \item Collected, managed, and analyzed survey data for economic and social studies.
\item Responsible for gathering information, analyzing data, and automating processes for economic and social studies.
\item Performed various system administration, automation, and scientific programming tasks using Python, SQL, Perl, and VBA.
\item Created complex web applications for data entry, tracking, and manipulation using R-shiny.
%\item Designed a small server environment for internal hosting from scratch, using Ubuntu Linux and Docker. Maintained said server and software stack, while training others to do the same.
\item Automated statistical analysis, including multi-variable regression, ANOVA, and Monte Carlo Simulation using R and Perl.
\item Worked with large relational databases, cleaning, proofing, and analyzing the data therein.
% %\bdot Acquired secondary data sets from corporate, government, and academic sources. \\
% \bdot Created multiple complex web applications for data entry, tracking, and manipulation using the R-shiny tool kit.\\
% \bdot Designed a server environment from scratch for internal hosting in the company, using Ubuntu and Docker.\\
% \bdot Maintained said server and software stack, while training others to do the same.\\
% \bdot Automated statistical analyses, including multi-variable regression, ANOVA, and Monte Carlo Simulation.\\
% \bdot Worked with large relational databases; cleaning, proofing and analyzing the data therein.
%\bdot Automated the mass production of reports and graphics making otherwise impossible tasks mundane.
\end{itemize}
}

\nonbox{
\job
{Cloud Operations Intern}
{May 2014 - Jan. 2015}
{Recondo Technology}
\begin{itemize}
\item Created various administrative programs using Ruby, BASH, PowerShell, and Puppet scripts.
%\item Tested scripts in a staging environment, and implemented them in production.
\item Maintained stage and prod Linux servers, implemented hardware and software, and managed databases.
% {\vspace{3pt} %Created various administrative programs using Ruby, BASH, Powershell, and Puppet scripts, then implemented those scripts in a staging environment. Created and implemented administrative programs using Ruby, BASH, Powershell, and Puppet script. Responsibilities included maintaining stage and production Red Hat servers.}
\end{itemize}
}

\vspace{-0.3cm}
