\documentclass[11pt,twoside]{letter}
\usepackage{carlletter}
\usepackage{lmodern}
\signature{Rory M. Flynn}
\address{
Rory M. Flynn\\
101 Reed Pl.\\
Longmont Co, 80504 \\\\
Phone: (970) 689 2239\\
Email: rmfofco@gmail.com\\
}


\begin{document}
\begin{letter}{}

%%%%%%%%%%
%  Note  %
%%%%%%%%%%
% Address the letter to a human name if possible
% Look up the contact and find out how to address them
% Make it clear why you are interested and what you can do to solve their problem in the opening paragraph.
% Then in the body give specifics. Times you did the things that they need done
% in the last repeat your interest and that you are the right person for the job
% don't make it too much longer

%%%%%%%%%%
% Needed %
%%%%%%%%%%
\newcommand{\jname}
{Workforce Data and Compliance Analyst opening}
\newcommand{\cname}
{HCPF}
  % {COMPNYNAMELONG}
\opening
{To whom it may concern at \cname{},}
\newcommand{\cnameshort}
{HCPF}
\newcommand{\mytitle}
 {Data Scientist, focused on Statistics, Software, and Visualization}
\newcommand{\opportunity}
  {}
\newcommand{\degree}
  % {Computer Science, with a focus in statistics and Data Science}
 {Computer Science focused in Data Science for Bio-medicine}
\newcommand{\class}
  {data analysis, collection, and visualization}
  % {Data Integration, Object-Oriented Software Development, and Simulation Design}
  % {Data Visualizations, Software Development, and Descriptive Modeling}
  % {feature detection, statistical analysis, and predictive modeling}
  % {data integration, data storage, and data processing}
  % C++ programming, and advanced software development


\setlength{\parindent}{15pt} % Default is 15pt.

Thank you for taking time to consider this application for the \jname{} at \cname{}.
I am a \mytitle{}.
% Opportunity
Currently, I am looking for a opportunity to apply my strong skill set in data
analytics for a higher cause, improving the health of the state and community I love and
that \cname{} helps
support.

With my education and work history, I am confident that I can meet all goals and expectations of the position.
I hold a Bachelor's of Statistics and a Master's of \degree{}.
Through my degrees, I have received formal training in \class{}.
Outside of academia, I have 5 years of experience in the research industry including at
government institutions, and government serving companies.
  % {large amounts of public code and maintained software environments for users
  % on the labs internal HPC, as well as the universities system}
Most recently, I have been embedded in the award-winning Wrighton Lab at CSU as a Researcher, and Software Engineer.
I have worked with experts in this extremely interdisciplinary team to collect,
validate and analyze data in order to answer complex questions about environmental
health.
I helped with all parts of the data collection and processing pipeline in the lab,
including helping with publications. I presented my work at conferences and to
my colleagues.
Before returning to graduate school, I worked as Researcher at BBC Research to fulfill government
contracts for Disparity Studies.


With this background, I have a deep understanding of the needs and challenges unique to
health and government data.
I continually strive to perfect skills, gain knowledge, and make work that I can be proud of.
I would be honored to do so as part of \cname.
  \closing{Sincerely,}


  % \ps{P.S.~Postscripts are optional.}
  % \encl{An optional enclosure.}
\end{letter}
\end{document}




